%% sec/failures.tex — §6 Failure-Mode Taxonomy
%% Source: paper/sec6_failures.md
%% NB: Table 4 frequency cells are TBD-from-D8 placeholders.

\section{Failure-Mode Taxonomy}
\label{sec:failures}

\subsection{Reframe --- bucket matrix, not case studies}
\label{sec:failures-reframe}

We reframe \S\ref{sec:failures} as an \textbf{11 LLM $\times$ 1
failure-probe spec bucket matrix}: a near-saturation variant of
the LC\_VCO\_20G spec contract that surfaces failure modes
comparably across vendors. At $\geq 5$ seeds per LLM, this is
\textbf{55+~runs} separate from the \S\ref{sec:results}
success-Pareto budget.

\subsection{Failure buckets}
\label{sec:failures-buckets}

Each failed run classifies into one of eight buckets, ordered by
the layer at which the failure surfaces:

\begin{description}
  \item[Empty-diff loop (stuck).] Design vector identical to the
    previous iteration; 3-iter stuck-streak guard aborts
    (\S\ref{sec:method-protocol} termination~(ii)).
  \item[Iteration-budget exhausted (wandering).] Vectors change
    but no all-metric-pass before \texttt{MAX\_ITER}
    (termination~(iii)); diagnostic-distinct from stuck
    (LLM-determinism vs search-strategy).
  \item[Contract-violation repair termination.] Tool call violates
    JSON contract; one repair-retry fails; run aborts.
  \item[\texttt{UNMEASURABLE} saturation.] Evaluator declares one
    or more metrics infeasible for several iterations running.
  \item[Topology-induced sanity-range FAIL.] Design vector outside
    the topology's physically reasonable range (e.g.\ tank
    inductance below process minimum).
  \item[PDK-content refusal (red-team probe).] Tool-call argument
    explicitly requests foundry content; blocked by
    \S\ref{sec:platform} scrub but counted as a failure event.
  \item[Reasoning-content replay.] PDK-tainted prior-tool-result
    content paraphrased inside the thinking channel; redacted
    re-entry path means no foundry tokens reach history, but the
    iteration is counted as anomalous (cross-link
    \S\ref{sec:platform-scrub} Tier~3).
  \item[Rate-limit / 429 cascade.] Provider rate-limits trip
    exponential back-off that halts iteration before budget cap.
\end{description}

\subsection{Bucket $\times$ LLM frequency matrix}
\label{sec:failures-matrix}

\begin{table*}[t]
  \centering
  \caption{Failure-bucket $\times$ LLM frequency matrix on the
    near-saturation probe spec. All cells are TBD-from-D8 counts;
    \tbdeight\ resolves the pre-registered hypotheses below.}
  \label{tab:failmatrix}
  \tiny
  \setlength{\tabcolsep}{3pt}
  \begin{tabular}{l c c c c c c c c c c c}
    \toprule
    \textbf{Bucket} & \textbf{Opus} & \textbf{Sonnet} & \textbf{Haiku} & \textbf{GPT-5.5} & \textbf{5.4-mini} & \textbf{Gemini} & \textbf{Kimi} & \textbf{MiniMax} & \textbf{MiMo} & \textbf{DS-pro} & \textbf{DS-flash} \\
    \midrule
    Empty-diff loop (stuck)        & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell \\
    Budget exhausted (wandering)   & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell \\
    Contract-violation repair      & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell \\
    \texttt{UNMEASURABLE} saturation & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell \\
    Topology sanity-range FAIL     & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell \\
    PDK-content refusal probe      & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell \\
    Reasoning-content replay       & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell \\
    Rate-limit / 429 cascade       & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell & \tbdcell \\
    \bottomrule
  \end{tabular}
\end{table*}

\subsection{Pre-registered hypotheses}
\label{sec:failures-hypotheses}

We \textbf{pre-register} the following predictions ahead of D8
data collection; Table~\ref{tab:failmatrix} will be marked
\yes/\no\ post-D8 independently of the SP3 Pareto findings.
Pre-registration converts the skeleton-before-data temporal
asymmetry from a defect into a methodological strength.

\begin{itemize}
  \item \textbf{H1.} Cost-floor checkpoints (Haiku 4.5,
    GPT-5.4-mini, DeepSeek V4-flash, MiMo v2.5-pro) will be
    over-represented in \emph{rate-limit / 429 cascade}.
  \item \textbf{H2.} Frontier checkpoints (Opus 4.7, GPT-5.5,
    Gemini 2.x) will be over-represented in
    \emph{\texttt{UNMEASURABLE} saturation} (deeper push into
    infeasible regions before giving up).
  \item \textbf{H3.} \emph{Reasoning-content replay} (closed by
    the e750189c patch on the re-entry leg) will be rarest on
    patched checkpoints; whether DeepSeek and MiMo behave
    equivalently is the open empirical question
    Table~\ref{tab:failmatrix} answers.
\end{itemize}
